---
title: "Project_Exploration"
author: "Brandon Keung"
date: "2024-03-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(bayesrules)
library(tidyverse)
library(tidybayes)
library(bayesplot)
library(rstanarm)
library(forcats)

# library(brms)
library(broom.mixed)
library(dplyr)
```

```{r}
#data <- read.csv("C:\\Users\\blkeu\\OneDrive\\Documents\\STATS115\\facebook+metrics\\dataset_Facebook.csv", sep=";")

data <- read.csv("data/dataset_Facebook.csv", sep = ";")


data$index <- seq_along(data$Page.total.likes)

data
```

```{r}
fb_data <- data %>% 
  select(index, Post.Month, Post.Weekday, Post.Hour, Total.Interactions, Lifetime.Engaged.Users, Type, Paid)

fb_data$Total.Interactions[fb_data$Total.Interactions == 0] <- 0.001

head(fb_data)
```

```{r}
# Graph of interactions by month for paid vs non-paid posts
plot_df <- fb_data

plot_df$Paid <- factor(plot_df$Paid)
plot_df$Post.Month <- factor(plot_df$Post.Month)

interaction_avg <- aggregate(Total.Interactions ~ Post.Month + Paid, data = plot_df, FUN = mean)

ggplot(interaction_avg, aes(x = Post.Month, y = Total.Interactions, color = factor(Paid), group = Paid)) +
  geom_line() +
  labs(title = "Average Post Interactions by Month and Paid Status",
       x = "Post Month", y = "Average Post Interactions", color = "Paid Status") +
  scale_color_manual(values = c("0" = "darkorange", "1" = "darkgreen"), 
                     labels = c("Not Paid", "Paid")) +
  theme_minimal()

```

```{r}
# Graph of interactions by weekday for paid vs non-paid posts
plot_df <- fb_data

plot_df$Paid <- factor(plot_df$Paid)
plot_df$Post.Weekday <- factor(plot_df$Post.Weekday)

interaction_avg <- aggregate(Total.Interactions ~ Post.Weekday + Paid, data = plot_df, FUN = mean)

ggplot(interaction_avg, aes(x = Post.Weekday, y = Total.Interactions, color = factor(Paid), group = Paid)) +
  geom_line() +
  labs(title = "Average Post Interactions by Weekday and Paid Status",
       x = "Post Weekday", y = "Average Post Interactions", color = "Paid Status") +
  scale_color_manual(values = c("0" = "darkorange", "1" = "darkgreen"), 
                     labels = c("Not Paid", "Paid")) +
  theme_minimal()

```
```{r}
# Graph of interactions by hour for paid vs non-paid posts
plot_df <- fb_data

plot_df$Paid <- factor(plot_df$Paid)
plot_df$Post.Hour <- factor(plot_df$Post.Hour)

interaction_avg <- aggregate(Total.Interactions ~ Post.Hour + Paid, data = plot_df, FUN = mean)

ggplot(interaction_avg, aes(x = Post.Hour, y = Total.Interactions, color = factor(Paid), group = Paid)) +
  geom_line() +
  labs(title = "Average Post Interactions by Hour and Paid Status",
       x = "Post Hour", y = "Average Post Interactions", color = "Paid Status") +
  scale_color_manual(values = c("0" = "darkorange", "1" = "darkgreen"), 
                     labels = c("Not Paid", "Paid")) +
  theme_minimal()

```

```{r}
# Graph of interactions by month for post types
plot_df <- fb_data

plot_df$Type <- factor(plot_df$Type)
plot_df$Post.Month <- factor(plot_df$Post.Month)

interaction_avg <- aggregate(Total.Interactions ~ Post.Month + Type, data = plot_df, FUN = mean)

ggplot(interaction_avg, aes(x = Post.Month, y = Total.Interactions, color = factor(Type), group = Type)) +
  geom_line() +
  labs(title = "Average Post Interactions by Month and Post Type",
       x = "Post Month", y = "Average Post Interactions", color = "Post Type") +
  #scale_color_manual(values = c("0" = "darkorange", "1" = "darkgreen"), 
   #                  labels = c("Not Paid", "Paid")) +
  theme_minimal()

```

```{r}
table(data$Type)
```

```{r}
# Graph of interactions by weekday for post types
plot_df <- fb_data

plot_df$Type <- factor(plot_df$Type)
plot_df$Post.Weekday <- factor(plot_df$Post.Weekday)

interaction_avg <- aggregate(Total.Interactions ~ Post.Weekday + Type, data = plot_df, FUN = mean)

ggplot(interaction_avg, aes(x = Post.Weekday, y = Total.Interactions, color = factor(Type), group = Type)) +
  geom_line() +
  labs(title = "Average Post Interactions by Weekday and Post Types",
       x = "Post Weekday", y = "Average Post Interactions", color = "Post Type") +
  #scale_color_manual(values = c("0" = "darkorange", "1" = "darkgreen"), 
   #                  labels = c("Not Paid", "Paid")) +
  theme_minimal()

```

```{r}
# Density plots for each post types
ggplot(data, aes(x = Total.Interactions, group = Type)) + 
  geom_density(aes(color = Type, fill = Type), alpha = 0.3) +
  xlim(c(0, 1000)) +
  labs(title = "Distribution of Interaction Counts by Post Type", x = "Total Interaction Count", y = "Density")
```


```{r}
# Graph of interactions by month for paid vs non-paid posts
plot_df <- fb_data

plot_df$Type <- factor(plot_df$Type)
plot_df$Post.Hour <- factor(plot_df$Post.Hour)

interaction_avg <- aggregate(Total.Interactions ~ Post.Hour + Type, data = plot_df, FUN = mean)

ggplot(interaction_avg, aes(x = Post.Hour, y = Total.Interactions, color = factor(Type), group = Type)) +
  geom_line() +
  labs(title = "Average Post Interactions by Hour and Paid Status",
       x = "Post Hour", y = "Average Post Interactions", color = "Post Type") +
  #scale_color_manual(values = c("0" = "darkorange", "1" = "darkgreen"), 
   #                  labels = c("Not Paid", "Paid")) +
  theme_minimal()

```

```{r}
fb_means <- fb_data %>% 
  group_by(Post.Month) %>% 
  summarize(count = n(), avg_interactions = mean(Total.Interactions))

fb_means
```

```{r}
fb_plot_data <- fb_data
fb_plot_data$Post.Month <- as.factor(fb_plot_data$Post.Month)
ggplot(fb_plot_data, aes(x = Total.Interactions, group = Post.Month)) + 
  geom_density(aes(color = Post.Month))
```

```{r}
mean(fb_data$Total.Interactions)
```

```{r}
fb_hierarchical <- stan_glmer(
  Total.Interactions ~ (1 | Post.Month), 
  data = data, family = neg_binomial_2,
  prior_intercept = normal(212.12, 100, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  prior_covariance = decov(reg = 1, conc = 1, shape = 1, scale = 1),
  chains = 4, iter = 5000*2, seed = 84735)

summary(fb_hierarchical)
```


```{r}
tidy(fb_hierarchical, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.80)

month_summary <- tidy(fb_hierarchical, effects = "ran_vals", 
                       conf.int = TRUE, conf.level = 0.80)

# Check out the results for the first & last 2 artists
month_summary %>% 
  select(level, conf.low, conf.high) %>% 
  slice(1:5)
```


```{r}
mcmc_trace(fb_hierarchical)
mcmc_acf(fb_hierarchical)
neff_ratio(fb_hierarchical)
rhat(fb_hierarchical)
```

```{r}
pp_check(fb_hierarchical)
```

```{r}
# Get MCMC chains
fb_chains <- fb_hierarchical %>%
  spread_draws(`(Intercept)`, b[,Post.Month]) %>% 
  mutate(mu_j = `(Intercept)` + b)

fb_chains %>% 
  select(Post.Month, `(Intercept)`, b, mu_j) %>% 
  head(4)
```

```{r}
# Get posterior summaries
fb_summary_scaled <- fb_chains %>% 
  select(-`(Intercept)`, -b) %>% 
  mean_qi(.width = 0.8) %>% 
  mutate(Post.Month = fct_reorder(Post.Month, mu_j),
         exp_mu_j = exp(mu_j),
         exp_lower = exp(.lower),
         exp_upper = exp(.upper))

fb_summary_scaled
```

```{r}
# Plot by INCREASING mu_j
ggplot(fb_summary_scaled, 
       aes(x = Post.Month, y = exp_mu_j, ymin = exp_lower, ymax = exp_upper)) +
  geom_pointrange() +
  xaxis_text(angle = 90, hjust = 1) +
  labs(title = "Mean Facebook Post Interaction Count by Month")

# Plot by MONTH ORDER
fb_summary_scaled$Month <- as.integer(gsub("Post.Month:", "", fb_summary_scaled$Post.Month))
ggplot(fb_summary_scaled, 
       aes(x = Month, y = exp_mu_j, ymin = exp_lower, ymax = exp_upper)) +
  geom_pointrange() +
  xaxis_text(angle = 90, hjust = 1) +
  labs(title = "Mean Facebook Post Interaction Count by Month")
```

```{r}
# Posterior prediction
set.seed(84735)
predictions_hierarchical <- posterior_predict(fb_hierarchical, newdata = fb_means)

# Posterior predictive plots
ppc_intervals(fb_means$avg_interactions, yrep = predictions_hierarchical, 
              prob_outer = 0.80) +
  ggplot2::scale_x_continuous(labels = fb_means$Post.Month, 
                              breaks = 1:nrow(fb_means)) +
  xaxis_text(angle = 90, hjust = 1) +
  geom_hline(yintercept = mean(fb_data$Total.Interactions), linetype = "dashed")

```

Hypothesis testing
Find the 95% CI for mu and check if all mu_j fall within the 95% CI
```{r}
posterior_interval(fb_hierarchical, prob = 0.95)
```

```{r}
fb_summary_scaled
```
$H_o$ = All $\mu_j$ are equal
$H_\alpha$ = The null hypothesis is not true.
With 95% CI for $\mu$ being (5.12211236, 5.5221324), Not all of the $\mu_j$ fall within this range. Therefore we can reject the null hypothesis and conclude that not all $\mu_j$ are equal.



EVERYTHING BELOW THIS MAY NOT BE USEFUL AS NEGATIVE BINOMIAL SEEMS LIKE THE RIGHT FAMILY TO USE




```{r}
fb2_hierarchical <- stan_glmer(
  Total.Interactions ~ Lifetime.Engaged.Users + (1 | Post.Month), 
  data = fb_data, family = Gamma,
  prior_intercept = normal(212.12, 2.5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  prior_covariance = decov(reg = 1, conc = 1, shape = 1, scale = 1),
  chains = 4, iter = 5000*2, seed = 84735)
```


```{r}
mcmc_trace(fb2_hierarchical)
mcmc_acf(fb2_hierarchical)
neff_ratio(fb2_hierarchical)
rhat(fb2_hierarchical)
```

```{r}
pp_check(fb2_hierarchical)
```


# Poisson regression - Ch. 12
```{r}
fb_data_poisson <- data
fb_data_poisson <- na.omit(fb_data_poisson)
fb_poisson_model_prior <- stan_glm(Total.Interactions ~ Post.Month + Paid, 
                                 data = fb_data_poisson, 
                                 family = poisson,
                                 prior_intercept = normal(212, 25),
                                 prior = normal(212, 25, autoscale = TRUE),
                                 chains = 4, iter = 5000*2, seed = 84735, 
                                 prior_PD = TRUE)

prior_summary(fb_poisson_model_prior)
```

```{r}
fb_data_poisson %>%
  add_fitted_draws(fb_poisson_model_prior, n = 100) %>%
  ggplot(aes(x = Post.Month, y = Total.Interactions, color = Paid)) +
    geom_line(aes(y = .value, group = paste(Paid, .draw))) + 
    ylim(0, 100)
```

```{r}
fb_poisson_model_prior <- update(fb_poisson_model_prior, prior_PD = FALSE)

mcmc_trace(fb_poisson_model_prior)
mcmc_dens_overlay(fb_poisson_model_prior)
mcmc_acf(fb_poisson_model_prior)
```

```{r}
# pp_check(fb_poisson_model_prior, plotfun = "hist", nreps = 5) + 
#   xlab("laws")
pp_check(fb_poisson_model_prior) + 
  xlab("laws")
```

```{r}
credible_intervals <- tidy(fb_poisson_model_prior, conf.int = TRUE, conf.level = 0.95)
# View the credible intervals
print(credible_intervals)
```






